\documentclass{article}
\title{Requirement Specification}
\author{Internship Group 6}
\begin{document}
\maketitle
\noindent
\textbf{Project Description:}\\
A web-based platform for AURAK to manage, archive, and showcase university events. It includes support for event creation, scheduling, media uploads (images/videos), and long-term archiving.
\par\noindent\rule{\textwidth}{0.5pt}
\textbf{Functional Requirements:}
\begin{description}
    \item[\textit{User Registration and Authentication:}] Users must be able to register, log in, and log out securely.
    \item[\textit{Event Creation:}] Event managers can create events with details like title, description, date, time, and location.
    \item[\textit{Media Upload:}] Event managers can upload images and videos related to events.
    \item[\textit{Event Scheduling:}] Event managers can schedule events on a calendar.
    \item[\textit{Event Archiving:}] Events can be archived for long-term storage.
    \item[\textit{Search Functionality:}] Users can search for past events by keywords or dates.
\end{description}
\par\noindent\rule{\textwidth}{0.5pt}
\textbf{Non-Functional Requirements:}
\begin{description}
    \item[\textit{Performance:}] The website needs to be responsive and able to handle up to 50 users concurrently.
    \item[\textit{Security:}] User data must be encrypted and secure against unauthorized access.
    \item[\textit{Usability:}] The interface should be intuitive and user-friendly, allowing users to navigate easily.
    \item[\textit{Scalability:}] The system should be able to scale to accommodate future growth in user base and data volume.
    \item[\textit{Deployability:}] The application should be deployable on the university's infrastructure or a cloud service.
    \end{description}
\par\noindent\rule{\textwidth}{0.5pt}
\end{document}